Incorporating Gyroscope Information in Gesture Recognition

### 2011-12-17 paper/paper.tex
fixed table again

\paragraph{HMM}
Although we found a few examples where the cluster-matching algorithm
benefits from using a Hidden Markov Model, in most real-world examples
there is little benefit.  When running on all of the training data,
we

\begin{center}
\begin{tabular}{ | l | l | l | l | l | }
  \hline
  Normalization & Features & Gestures Types & Accuracy \\ \hline
  Yes	&	Both  &	All &	94.6\% \\ \hline
  Yes	&	Both	&	All &	89.6\% \\ \hline
  Yes	&	Accel &	All &	92.0\% \\ \hline
  Yes	&	Accel &	All &	84.2\% \\ \hline
  Yes	&	Gyro  &	All &	92.3\% \\ \hline
  Yes	&	Gyro  &	All &	89.7\% \\ \hline
  Yes	&	Both	&	All &	96.7\% \\ \hline
  Yes	&	Both	&	All &	97.9\% \\ \hline
  Yes	&	Both  &	All &	98.4\% \\ \hline
  No	&	Both	&	All &	98.4\% \\ \hline
  Yes	&	Both	& Squares &	100\% \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	Chance \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	72.0\% \\ \hline
  Yes	&	Both  & Circles and Reversed-circles  &	88.8\% \\
  \hline
\end{tabular}
\end{center}

>>>>

\paragraph{HMM}
Although we found a few examples where the cluster-matching algorithm
benefits from using a Hidden Markov Model, in most real-world examples
there is little benefit.  When running on all of the training data,
we found that adding the HMM actually decreased accuracy slightly,
from 96.7\% to 94.6\%

\begin{center}
\begin{tabular}{ | l | l | l | l | l | }
  \hline
  Normalization & Features & Algorithm & Gestures Types & Accuracy \\ \hline
  Yes	&	Both  &	All & Cluster-matching with HMM (10) &	94.6\% \\ \hline
  Yes	&	Both	&	All & Original  &	89.6\% \\ \hline
  Yes	&	Accel &	All & Cluster-matching with HMM (10) &	92.0\% \\ \hline
  Yes	&	Accel &	All &	Original & 84.2\% \\ \hline
  Yes	&	Gyro  &	All & Cluster-matching with HMM (10) & 92.3\% \\ \hline
  Yes	&	Gyro  &	All & Original &  89.7\% \\ \hline
  Yes	&	Both	&	All &	Cluster-matching (10) &  96.7\% \\ \hline
  Yes	&	Both	&	All &	Cluster-matching (20) &  97.9\% \\ \hline
  Yes	&	Both  &	All &	Cluster-matching (40) & 	98.4\% \\ \hline
  No	&	Both	&	All &	Cluster-matching (40) & 	98.4\% \\ \hline
  Yes	&	Both	& Squares &	Cluster-matching (10) & 	100\% \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	Cluster-matching (10) & 	Chance \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	Cluster-matching with HMM (10) &	72.0\% \\ \hline
  Yes	&	Both  & Circles and Reversed-circles  &	Cluster-matching with HMM (20) & 88.8\% \\
  \hline
\end{tabular}
\end{center}
